---
title: "Hobbies and Goals"
---
```{r setup, include=FALSE}
# import packages ----
library(tidyverse) # data wrangling & viz (with {ggplot2})
library(plotly) # JS plots!
library(DT) # JS tables!
library(leaflet) # JS maps!
library(leaflet.extras) # leaflet add-ons!
```

## My Hobbies and Goals

# National Parks

I have always been interested in nature and the environment, and I attribute this to my dad, who has traveled with me to every National Park in California and Utah, as well as a few others. I have made it a life mission of mine to visit every National Park in the United States.
```{r}
#| echo: false
parks <- data.frame(
  name = c(
    # California National Parks
    "Yosemite National Park",
    "Sequoia National Park",
    "Kings Canyon National Park",
    "Death Valley National Park",
    "Joshua Tree National Park",
    "Lassen Volcanic National Park",
    "Redwood National Park",
    "Channel Islands National Park",

    # Utah National Parks
    "Zion National Park",
    "Bryce Canyon National Park",
    "Arches National Park",
    "Canyonlands National Park",
    "Capitol Reef National Park",

    # Arizona
    "Grand Canyon National Park",
    "Petrified Forest National Park"
  ),

  lat = c(
    # CA
    37.8651, 36.4864, 36.8879, 36.5323, 33.8734, 40.4977, 41.2132, 34.0069,

    # UT
    37.2982, 37.5930, 38.7331, 38.3269, 38.2919,

    # AZ
    36.1069, 34.9099
  ),

  lng = c(
    # CA
    -119.5383, -118.5658, -118.5551, -116.9325, -115.9010, -121.5050, -124.0046, -119.9113,

    # UT
    -113.0263, -112.1871, -109.5925, -109.8783, -111.2615,

    # AZ
    -112.1129, -109.8068
  )
)
```

```{r}
#| echo: false
leaflet(parks) |>
  addProviderTiles("CartoDB.Positron") |>
  addCircleMarkers(
    lng = ~lng,
    lat = ~lat,
    radius = 6,
    color = "blue",
    stroke = TRUE,
    fillOpacity = 0.7,
    popup = ~name
  ) |>
  setView(lng = -112, lat = 38, zoom = 5)
```
This map shows the locations and names of every National Park I have visited.

# Competitive Gaming

I have been a fan of Pokemon since I was in preschool, playing the games and trading cards with friends. In the past year, I have started playing competitive Pokemon TCG, attending local events, ranging from casual tournaments to competitive Cups and Challenges. Currently, my highest placements at these events were a 2nd place at a 15 person Challenge and a 5th place at a 30 person Challenge. I have also further challenged myself by not playing the game with the best deck in the game, but with the decks I enjoy most. 

I also have competed in Collegiate League of Legends, serving both as a team member and as team captain of the Glendale Community College Vaqueros League of Legends Team. Organizing practices, scrimmages against other teams, reviewing play, and helping my team improve were just a few of my responsibilities in this role. Over time, I have worked to greatly improve my own skills as well, now ranking in the top 20% of North American players.



